---
title: "Scrabble Exercise"
author: "Parola Alberto"
date: "14/02/2022"
output: html_document
---


Exercise 1) 
- Load the three datasets (two individual rounds and one collaboration round)
- Run cleaning 
- Calculate the number of same words (provided), same-words-ratio, similarity and collective benefit 
- Did your group perform better than the best individual? 

```{r}

pacman::p_load(
  tidyverse,
  here
)
tidyverse_deps(recursive = FALSE, repos = getOption("repos"))

rm(list=ls())

devtools::install_github("tidyverse/tidyverse")


d1 <- read_csv("data")
d2 <- read_csv("data2")
d3 <- read.csv("data3")

###Clean up 

#Remove incorrect words 
d1 = d1[d1$Validity ==1,]
d2 = d2[d2$Validity == 1,]
d3 = d3[d3$Validity == 1,]

#Remove duplicates 
d1 <- d1[!duplicated(d1[,'Word']),]
d2 <- d2[!duplicated(d2[,'Word']),]
d3 <- d3[!duplicated(d3[,'Word']),]

######################## Calculations #########################

#Same words (produced by each individual)

same_words <- 0

for (i in 1:nrow(d1)){
  if (d1$Word[i] %in% d2$Word){
    same_words = same_words+1
  }
}
same_words <- same_words

#Same-words ratio 

#Similarity 

#Collective benefit 


```


Exercise 2) 

Load the three datasets in the zip folder (round1.csv, round2.csv, round3.csv)

Create linear models investigating hypotheses you find interesting regarding: 
 - effects on Collective Benefit 
 - effects on Diversity 
 - effects on Similarity 
 - Did collaboration change the diversity/similarity of the pairs? (use data from round 3)

Create plots to inspect the results.  

```{r setup, include=FALSE}
###Load data 
#Round 1) Individual task 
d1 <- read.csv("round1.csv")

#Round 2) Group task 
d2 <- read.csv("round2.csv")

#Round 3) Individual performance combined into groups 
d3 <- read.csv("round3.csv")

#Are groups better than the best of individuals? Is collective benefit > 1?
m1 <- lm(CollectiveBenefit-1~1, d2)
summary(m1) # Nope


test <- seq(1,5)

```


